### 2013-09-20 evaluation/paper.tex
experiment stuff

\subsection{Superpixel CRFs for Semantic Segmentation}

>>>>

\subsection{Superpixel CRFs for Semantic Segmentation}
Our main attention is devoted to the use of conditional random fields for
semantic segmentation.  We use the Pascal VOC and MSRC datasets. A detailed
description of the method will be given in Chapter~\ref{ch:exact_learning}.
%TODO will it?
The Pascal VOC has \ldots training and \ldots test images, each having
around 100 superpixels. There are 20 object categories, plus background. The % TODO check!
MSRC dataset has \ldots training and \ldots test images, also segmented in
around 100 superpixels each. We use the MSRC-21 dataset, which has 21 target
classes.
Each superpixel is represented as an output variable, with the ground truth obtained
by majority vote over the pixel belonging to the superpixel.
Pairwise potentials were introduced for each pair of neighboring superpixels.
We then removed all superpixels that were labeled as ``void'', together with
their pairwise potentials.
As unary potentials, we use the TextonBoost probabilities provided by \citet{krahenbuhl2012efficient}.
We average probabilities inside each superpixel, yielding 21 input features for both datasets.
We also used the same pairwise features for the two datasets: a constant feature,
a color contrast feature, and a feature encoding relative vertical position between superpixels.
Overall, the models for both datasets had $21 \cdot 21 + 21^2 \cdot 4$ features.
It is possible to assume symmetric potentials for this dataset, leading to less
pairwise features.  We found both parametrizations yielded similar results.

\section{Experiments}
We compare the following algorithms on the above models:
\begin{itemize}
    \item Stochastic Subgradient Descent using the Pegasos schedule: %TODO
    \item Stochastic Subgradient Descent using a momentum heuristic:
    %\item Stochastic Subgradient Descent using a momentum heuristic: AVERAGING
    %\item Stochastic Subgradient Descent using a momentum heuristic: AVERAGING
    \item The $1$-slack cutting plane algorithm without constraint caching.
    \item The $1$-slack cutting plane algorithm with constraint caching. For
            each sample, the last $50$ inference results are stored.
            Details of the caching strategy can be found in Chapter~\ref{ch:exact_learning}.
            %TODO
    \item The $n$-slack cutting plane algorithm, where the QP is solved after each training.
    \item The $n$-slack cutting plane algorithm, where the QP is solved every 100 training samples.
    \item The SZLJSP algorithm.
\end{itemize}
All algorithm take a $C$ parameter, which we adjusted on a fully trained model
on a validation set (experiments not reported here) and held constant for all models.
We found, however, that the algorithms and models are quite robust to the choice of $C$ within
one or two orders of magnitude.
As stopping criterion, we used a duality gap of $0.1$ when possible, and a pre-defined
number of iterations for the subgradient algorithms.

Our ultimate evaluation criterion is how fast the learning algorithms converge,
and how robust they are to approximate inference.  To quantify our goals, we
track primal suboptimality and training set error during learning, as well as
final error on the test set.
We report suboptimality as a function of runtime, and as a function of passes over the training set.
Both are important to practitioners, as they give important insight into the workins of the algorithm.
The actual runtime is certainly the most important factor, but also highly influenced by implementation details
and properties of the dataset. We are particularly interested in cases where inference is highly non-trivial.
In these cases, inference
